---
title: "1. Sealing the R Objects Test and Assert Conditions"
author: "Shinya Uryu"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    toc: true
    number_sections: true
vignette: >
  %\VignetteIndexEntry{1. Sealing the R Objects Test and Assert Conditions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Motivation

Data is not always what you think. Someone may change a single value or the data type may be different depending on the specification the API. We need to be aware of these data changes as soon as possible (*It is hard to review from the final result!*).

You can use tests and asserts to check data behavior. Although the testthat package is originally used for unit test of R package, this framework is wide and applicable to any *R* object. On the other hand, it is time-consuming task to enter the state of existing objects, and there is a possibility of mistakes as well.

The goal of **sealr** is to reduce the burden of writing unit tests and assertion that record the state of objects. Applying a function of sealr to the target object outputs the test code that record the current state.

## How to use

1. (As usual) Create an *R* object.
2. Execute the function of sealr (`design_*()` or `transcribe()`) against a object whose state is to be record.
    - `design_*()`... The preamble is fixed and consists of the function name bearing test items (eg. `design_class()`, `design_length()`, etc.).
    - `transcribe()`... Sets of `design_*()`.It is a generic function and returns combinations according to the class of the object.

```{r, eval = TRUE, echo = TRUE}
library(sealr)
library(testthat)
```

```{r}
x <- seq(1, 9, by = 2)

design_class(x, seal = TRUE)

design_range(x, seal = TRUE)
```

You can copy the output, but if you activate the *clip* argument, the output result will be in a copied state, pasting that value is too easy. This feature depends on the [clipr](https://github.com/mdlincoln/clipr) package.

```{r, eval = FALSE, echo = TRUE}
design_class(x, seal = TRUE, clip = TRUE)
expect_is(
  x,
  "numeric"
)
```

`transcribe()` is a generic function that produces output according to the class of the object. Currently it suports to 8 classes, but we plan to add various classes in future upgrades.

```{r, warning = FALSE}
transcribe(iris)

my_data <- list(A = letters, B = trees)

transcribe(my_data, load_testthat = FALSE, ts = FALSE)
```

## Details

### Options

Both `design_*()` and `transcribe()` have the following common arguments (Ref. `?seal`).

- load_testthat: include `library(testthat)` when *TRUE*
- clip: If *TRUE* will overwrite the system clipboard. When clipr is not available, The clip arguments is forcibly *FALSE*.
- ts: include comments that timestamp?
- mask_seal: Whether to comment out after executing the function. Default FALSE. This option is effective only when using RStudio.

### APIs

#### design_* function

- `design_class()`
- `design_length()`

#### transcribe function

Suports to 8 classes. Default test of the class. 

- numeric
- character
- factor
- Date
- data.frame
- list
- matrix
- table
